### 2013-08-14 pystruct/paper.tex
update jmlr paper in thesis

\section{Introduction}
In recent years there has been a wealth of research in methods for learning structured prediction,
as well as in applications such as natural language processing and computer vision.
Unfortunately only few implementations are publicly available, and many applications build upon
the non-free implementation of~\citet{joachims2009cutting}.

\pystruct on the other hand aims at providing a simple-to-use interface, in the high-level Python language.
This allows practitioners to efficiently test a range of models, as well as allowing researchers
to compare to baseline methods much more easily.
\pystruct is BSD-Licensed, allowing modification and redistribution of the code,
as well as use in commercial applications.  By embracing paradimes established
in the scientific python community, and reusing the interface of the
widely-used {\sc scikit-learn} library~\citep{pedregosa2011scikit}, \pystruct
can be used in existing projects, replacing standard classifiers.
The online documentation and examples help new
users understand the somewhat abstract ideas behind structured pediction.

@@

Structured prediction can be defined as making a prediction $f(x)$ by maximizing an
compatibility function $g$ between an input $x$ and the possible labels
$y$~\citep{nowozin2011structured}. Most current approaches use linear functions,
leading to:
\begin{equation}\label{eq:main_equation}
    f(x) = \argmax_{y \in \mathcal{Y}} \langle \theta, \Psi(x, y) \rangle 
\end{equation}
Here, $y$ is a \emph{structured} label in the sense that it is more complicated than a single
output class. Examples include predicting a label for each word in a sentence, or predicting
a label for each pixel in an image.
Learning structured prediction means learning the parameters $\theta$ from training data
$(x_1, y_1), \dotsc, (x_n, y_n)$.

Using the above formulation learning can be broken down into three sub-problems:
\begin{itemize}
    \item Optimizing the objective with respect to $\theta$.
    \item Encoding the structure of the problem in a joint features function $\Psi$.
    \item Solving the maximization problem in Equation~\ref{eq:main_equation}.
\end{itemize}

The later two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Psi$, while the first one is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2) and 3) from the general algorithms used to solve 1).

Parameter estimation is done in \texttt{learner} classes, which currently support
cutting plane algorithms for structural SVMs (SSVMs), subgradient methods for SSVMs,
the structured perceptron and latent variable SSVMs.
Encoding the structure of the problem is done using \texttt{model} classes, that
compute $\Psi$, and encode the structure of the problem.
\pystruct implements models for many common cases, such as multi-class and
multi-label classification, conditional random fields with constant or
data-dependent pairwise potentials, and several latent variable models.
The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes direct support for using {\sc OpenGM}, {\sc LibDAI}~\citep{Mooij_libDAI_10} and {\sc
AD$^3$}~\citep{martins2011augmented}. It also includes an interface to a
general purpose linear programming solver.

Table~\ref{table:comparision} lists implemented algorithms and models, and
compares them to other public structured prediction libraries, together with
the programming language and the project license.

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccccccc}
\toprule
Package &     Language &     License&\multicolumn{4}{c}{Algorithms}&\multicolumn{3}{c}{Models} \\
\cmidrule(r){1-1} \cmidrule(r){2-2} \cmidrule(r){3-3} \cmidrule(r){4-7} \cmidrule{8-10}
&             &&                     \footnotesize{CP}& \footnotesize{SG}& \footnotesize{LV}& \footnotesize{ML}& \footnotesize{Chain} & \footnotesize{Graph} & \footnotesize{LDCRF}\\
\sc{\pystruct}&      Python &       BSD            & \x    & \x      & \x   & \o & \x     & \x     & \x \\
SVM$^\text{\sc{struct}}$ & C++ & non-free         & \x    & \o      & \x   & \o & \o     & \o     & \o \\
\sc{Dlib}         & C++        & boost            & \x    & \x      & \o   & \o & \x     & \x     &\o\\
\sc{CRFsuite}     & C++        & BSD              & \o    & \o      & \o   & \x & \x     & \o     &\o\\

\bottomrule
\end{tabularx}
    \caption{Comparison of structured prediction software packages. CP stands
for cutting plane optimization of SSVMs~\citep{joachims2009cutting}, SG for
online subgradient optimization of SSVMs~\citep{ratliff2007online}, LV for
latent variable SSVMs~\citep{yu2009learning}, ML for maximum likelihood
training, Chain for chain-structured models
with pairwise interactionsr, Graph for arbitrary graphs with pairwise
interactions, and LDCRF for latent dynamic CRF~\citep{morency2007latent}.\label{table:comparision}}
\end{table}

@@

\paragraph{Completeness}\pystruct aims at providing full pipelines that can be
    used in applications. It contains model formulation for many typical
    applications.  This is in contrast to SVM$^\text{struct}$ that provides no
    models at all, requiring the user to develop siginificant amounts of code, even
    for simple tasks.

\paragraph{Modularity} \pystruct separates the algorithms of parameter estimation and
     inference from the task-dependent formulation of $\Psi$. This allows
     practictioners, for example in computer vision or natural language
     processing, to improve their model without changing any optimization
     code. On the other hand, researchers working on better inference or
     parameter learning can easily benchmark their improvements on a wide
     array of applications.

@@

\paragraph{Documentation and Examples}
     \pystruct provides full documentation of all classes and functions.  It
     also provides examples for many important applications, such as
     sequence tagging, multi-label classification and image segmentation.
     Furthermore, standard benchmarks are included as examples, which allows
     easy comparision with other approaches.

@@

\paragraph{Integration}
     To improve usability, \pystruct is interoperable with other numeric and scientific python projects,
     such as {\sc scikit-learn}~\citep{pedregosa2011scikit},
     {\sc mahotas}~\citep{coelho:mahotas}, {\sc gensim}~\citep{rehurek_lrec} and {\sc scikit-image}.
     This allows users to build powerful applications with little effort. In
     particular, most of the model-selection methods of scikit-learn can be used
     directly with \pystruct.

\section{Usage Example: Semantic Image Segmentation}\label{sec:examples}
%\subsection{Multi-class classification}
%Multi-class classification is a very simple case of structured prediction, that serves
%well to exemplify the usage. We load the iris dataset, and compare the usage of \pystruct
%with a call to LibLinears Crammer-Singer SVM using scikit-learn.
%\lstinputlisting[language=Python, frame=single, basicstyle=\scriptsize,
    %numbers=left, commentstyle=\color{blue}\normalfont,
%columns=flexible, firstline=11]{multi_class_example.py}

%\subsection{OCR sequence classification}
%Chain structured CRFs are commonly used in natural language processif, for
%example for part-of-speech tagging or named entity recognition.  Here we
%demonstrate the use of a chain CRF on the OCR dataset from. The ChainCRF provides
%a very simnple interface for this problem. Each example is presented as an
%array of input features of shape % (length_of_sequence, number_of_features).
%% listing, training time, accuracy, comparision with kraehenbuehl

\subsection{Semantic Image Segmentation}
Conditional random fields are an important tool for semantic image segmentation.
We show how to train an $n$-slack support vector machines on a superpixel-based CRF
on the popular Pascal dataset. We use unary potentials generated using TextonBoost
from \cite{krahenbuhl2012efficient}. The superpixels are generated using SLIC.%
\footnote{The preprocessed data can be downloaded at \dots.}
Each sample is represented as a tuple consisting of input features and a graph representation.

\lstinputlisting[language=Python, frame=single, basicstyle=\scriptsize,
    numbers=left, commentstyle=\color{blue}\normalfont,
columns=flexible,firstline=32, lastline=37]{pascal_crf.py}
Lines 1-3 declare a quite complex model pairwise model on an arbitray graph.
Here \texttt{class\_weight} reweights the hamming loss according to class
frequencies. The parametric pairwise interactions have three features: a
constant feature, color similarity, and relative vertical position. The first
are declared to be symmetric with respect to the direction of an edge, the last
is antisymmetric. The inference method used is QPBO-fustion moves.  Line 5
creates an \texttt{learner} object that will learn the parameters for the given
model using the n-slack cutting plane method, and line 6 performs the actual
learning.  Using this simple setup, we achieve an accuracy of 30.3 on the
valiation set following the setup of \citet{krahenbuhl2012efficient}, who
report 30.2 using a more complex approach. Training the structured model takes
approximately 30 minutes using a single i7 core (using more would be possible).

%TODO not here
%This makes it very easy to incoporate features or segments generated by computer vision libraries such
%as scikit-image or mahotas, and to plot results using visualization tools like matplotlib. 
% listing, training time, accuracy, comparision with kraehenbuehl

\section{Experiments}\label{sec:benchmarks}
In this section, we compare our implementation with SVM$~\text{multiclass}$ and
SVM$~\text{python}$ with respect to run-time and optimzation accuracy.
While SVM$~\text{python}$ allows integration with Python programs, it does not use native
Python data structures, such as Numpy arrays. This makes interacting with existing software
cumbersome and inefficient, which is reflected in the run-time comparision below.
We also compare against the special-purpose implementation of the Crammer-Singer multi-class SVM in
{\sc LibLinear}~\citep{fan2008liblinear}.

We do not provide comparisions on more complex problems--such as ones including
non-trivial inference--as the authors of SVM$^\text{struct}$ did not provide
any code or examples for this case.

MNIST, covertype?

% multiclass on mnist? liblinear seems to die!!!!

\section{Conclusion}
This paper introduced \pystruct, a modular structured learning and prediction library.
\pystruct is geared towards ease of use, while providing efficient implementations.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently \pystruct focuses on max-margin and perceptron based approaches. In the future,
we plan to integrate other paradigms, such as SampleRank, pseudo-likelihood learning,
Conditional Neural Fields and approaches that allow for a better integration of inference
and learning.

>>>>

In recent years there has been a wealth of research in methods for learning structured prediction,
as well as in their application in areas such as natural language processing and computer vision.
Unfortunately only few implementations are publicly available---many applications are based on
the non-free implementation of~\citet{joachims2009cutting}.

\pystruct aims at providing a high-quality implementation with an easy-to-use
interface, in the high-level Python language.  This allows practitioners to
efficiently test a range of models, as well as allowing researchers to compare
to baseline methods much more easily than this is possible with current
implementations.  \pystruct is BSD-licensed, allowing modification and
redistribution of the code, as well as use in commercial applications.  By
embracing paradigms established in the scientific Python community and reusing
the interface of the widely-used {\sc scikit-learn}
library~\citep{pedregosa2011scikit}, \pystruct can be used in existing
projects, replacing standard classifiers.  The online documentation and
examples help new users understand the somewhat abstract ideas behind
structured prediction.

@@

Structured prediction can be defined as making a prediction $f(x)$ by maximizing a
compati\-bility function between an input $x$ and the possible labels
$y$~\citep{nowozin2011structured}. Most current approaches use linear functions,
leading to:
\begin{equation}\label{eq:main_equation}
    f(x) = \argmax_{y \in \mathcal{Y}}\  \theta^T \Psi(x, y).
\end{equation}
Here, $y$ is a \emph{structured} label, $\Psi$ is a joint feature function of $x$ and $y$, and
$\theta$ are parameters of the model. \emph{Structured} means that $y$ is more complicated than a single
output class, for example a label for each word in a sentence or a label for
each pixel in an image.
Learning structured prediction means learning the parameters $\theta$ from training data.

Using the above formulation, learning can be broken down into three sub-problems:
\begin{enumerate*}
    \item Optimizing the objective with respect to $\theta$.
    \item Encoding the structure of the problem in a joint feature function $\Psi$.
    \item Solving the maximization problem in Equation~\ref{eq:main_equation}.
\end{enumerate*}
The later two problems are usually tightly coupled, as the maximization in
Equation~\ref{eq:main_equation} is usually only feasible by exploiting the
structure of $\Psi$, while the first one is usually treated as independent.
\pystruct takes an object-oriented approach to decouple the task-dependent
implementation of 2. and 3. from the general algorithms used to solve 1.

Estimating $\theta$ is done in \texttt{learner} classes, which currently support
cutting plane algorithms for structural support vector machines~(SSVMs), subgradient methods for SSVMs,
the structured perceptron and latent variable SSVMs. The cutting plane implementation uses the {\sc cvxopt} package \citep{dahl2006cvxopt}
for quadratic optimization.
Encoding the structure of the problem is done using \texttt{model} classes, which
compute $\Psi$ and encode the structure of the problem.
\pystruct implements models for many common cases, such as multi-class and
multi-label classification, conditional random fields with constant or
data-dependent pairwise potentials, and several latent variable models.
The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes support for using {\sc OpenGM}~\citep{kappes2013comparative}, {\sc
LibDAI}~\citep{Mooij_libDAI_10}, QPBO fusion moves~\citep{rother2007optimizing},
and {\sc AD$^3$}~\citep{martins2011augmented}. It also includes an interface to
a general purpose linear programming solver from \textsc{cvxopt}~\cite{dahl2006cvxopt}.

Table~\ref{table:comparision} lists algorithms and models that are implemented in \pystruct and
compares them to other public structured prediction libraries, together with
the programming language and the project license.

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccccccc}
\toprule
Package &     Language &     License&\multicolumn{4}{c}{Algorithms}&\multicolumn{3}{c}{Models} \\
\cmidrule(r){1-1} \cmidrule(r){2-2} \cmidrule(r){3-3} \cmidrule(r){4-7} \cmidrule{8-10}
&             &&                     \footnotesize{CP}& \footnotesize{SG}& \footnotesize{LV}& \footnotesize{ML}& \footnotesize{Chain} & \footnotesize{Graph} & \footnotesize{LDCRF}\\
\pystruct&      Python &       BSD$^1$  & \x$^1$    & \x      & \x   & \o & \x     & \x     & \x \\
\svmstruct & C++ & non-free         & \x    & \o      & \x   & \o & \o     & \o     & \o \\
\sc{Dlib}         & C++        & boost            & \x    & \x      & \o   & \o & \x     & \x     &\o\\
\sc{CRFsuite}     & C++        & BSD              & \o    & \o      & \o   & \x & \x     & \o     &\o\\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision}Comparison of structured prediction software packages. CP stands
for cutting plane optimization of SSVMs~\citep{joachims2009cutting}, SG for
online subgradient optimization of SSVMs~\citep{ratliff2007online}, LV for
latent variable SSVMs~\citep{yu2009learning}, ML for maximum likelihood
learning, Chain for chain-structured models
with pairwise interactions, Graph for arbitrary graphs with pairwise
interactions, and LDCRF for latent dynamic CRF~\citep{morency2007latent}.
{\footnotesize $^1$\pystruct itself is BSD licensed, but uses the GPL-licensed package {\sc cvxopt} for cutting-plane learning.}
}
\end{table}
\vfill
\pagebreak

@@

\paragraph{Completeness}\pystruct aims at providing full pipelines that can be
    used in applications. It contains model formulation for many typical
    applications.  This is in contrast to \svmstruct that provides no
    models at all, requiring the user to develop significant amounts of code, even
    for simple tasks.

\paragraph{Modularity} \pystruct separates the algorithms of parameter estimation and
     inference from the task-dependent formulation of $\Psi$. This allows
     practitioners, for example in computer vision or natural language
     processing, to improve their model without changing any optimization
     code. On the other hand, researchers working on better inference or
     parameter learning can easily benchmark their improvements on a wide
     array of applications.

@@

\paragraph{Documentation and Examples}
     \pystruct provides full documentation of all classes and functions.  It
     also provides examples for many important applications, such as
     sequence tagging, multi-label classification and image segmentation.
     Furthermore, standard benchmarks are included as examples, which allows
     easy comparison with the literature.

@@

\paragraph{Integration}
     To improve usability, \pystruct is interoperable with other numeric and scientific Python projects,
     such as {\sc scikit-learn}~\citep{pedregosa2011scikit},
     {\sc mahotas}~\citep{coelho:mahotas}, {\sc gensim}~\citep{rehurek_lrec}, and {\sc scikit-image}.
     This allows users to build powerful applications with little effort. In
     particular, most of the model-selection methods of {\sc scikit-learn} can be used
     directly with \pystruct.

\section{Usage Example: Semantic Image Segmentation}\label{sec:examples}
%\subsection{Multi-class classification}
%Multi-class classification is a very simple case of structured prediction, that serves
%well to exemplify the usage. We load the iris dataset and compare the usage of \pystruct
%with a call to LibLinears Crammer-Singer SVM using scikit-learn.
%\lstinputlisting[language=Python, frame=single, basicstyle=\scriptsize,
    %numbers=left, commentstyle=\color{blue}\normalfont,
%columns=flexible, firstline=11]{multi_class_example.py}
%\subsection{OCR sequence classification}
%Chain structured CRFs are commonly used in natural language processif, for
%example for part-of-speech tagging or named entity recognition.  Here we
%demonstrate the use of a chain CRF on the OCR dataset from. The ChainCRF provides
%a very simnple interface for this problem. Each example is presented as an
%array of input features of shape % (length_of_sequence, number_of_features).
%% listing, training time, accuracy, comparision with kraehenbuehl

Conditional random fields are an important tool for semantic image
segmentation.  We demonstrate how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. We use
unary potentials generated using TextonBoost
from \citet{krahenbuhl2012efficient}. The superpixels are generated using SLIC~\citep{achanta2012slic}.%
\footnote{The preprocessed data can be downloaded at \url{http://www.ais.uni-bonn.de/download/datasets.html}.}
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
    class_weight=inverse_frequency, symmetric_edge_features=[0, 1],
    antisymmetric_edge_features=[2], inference_method='qpbo')

ssvm = learners.NSlackSSVM(model, C=0.01, n_jobs=-1)
ssvm.fit(X, Y)
\end{pythoncode}
\caption{Example of defining and learning a CRF model.\label{lst:stuff}}
\end{listing}

The source code is shown in Listing 1.
Lines 1-3 declare a model using parametric edge potentials for arbitrary graphs.
Here \texttt{class\_weight} re-weights the hamming loss according to inverse class
frequencies. The parametric pairwise interactions have three features: a
constant feature, color similarity, and relative vertical position. The first two
are declared to be symmetric with respect to the direction of an edge, the last
is antisymmetric. The inference method used is QPBO-fusion moves.  Line 5
creates a \texttt{learner} object that will learn the parameters for the given
model using the n-slack cutting plane method, and line 6 performs the actual
learning.  Using this simple setup, we achieve an accuracy of 30.3 on the
validation set following the protocol of \citet{krahenbuhl2012efficient}, who
report 30.2 using a more complex approach. Training the structured model takes
approximately 30 minutes using a single i7 core.

\section{Experiments}\label{sec:benchmarks}
While \pystruct focuses on usability and covers a wide range of applications, it is also
important that the implemented learning algorithms run in acceptable time.
In this section, we compare our implementation of the one-slack cutting plance
algorithm with the implementation in \svmstruct.
We compare performance of the Crammer-Singer multi-class SVM with respect to
learning time and accuracy on the MNIST dataset of handwritten digits.
While multi-class classification is not very interesting from a structured
prediction point of view, this problem is well-suited to benchmark the cutting
plane solvers with respect to accuracy and speed.

Results are shown in \Figref{timings}. We report learning times and accuracy for
varying regularization parameter $C$. The MNIST dataset has 60\,000 training
examples, 784 features and 10 classes.%
\footnote{Details about the experiment and code for the experiments can be found on the project website.}
The figure indicates that \pystruct has competitive performance, while using
a high-level interface in a dynamic programming language.

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{times_MNIST}
\includegraphics[width=.45\textwidth]{accs_MNIST}
\caption{Runtime comparison of \pystruct and \svmstruct for multi-class
    classification.
}
\label{fig:timings}
\end{figure}

\section{Conclusion}
This paper introduced \pystruct, a modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches. In the future,
we plan to integrate other paradigms, such as sampling-based learning~\citep{wick2011samplerank},
surrogate objectives (for example pseudo-likelihood), and approaches that allow for a better integration
of inference and learning~\citep{meshi2010learning}.
